Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-10-29 bbbq_article.tex
Added IEDB to methods, progress #229

To obtain experimental evidence that epitopes derived from TMHs are presented in MHC, 
peptide elution studies for MHC-I \cite{schellens2015comprehensive} 
and MHC-II \cite{bergseng2015different} were reanalyzed.
For each of the detected epitopes,
its possible location(s) in 
a human reference proteome,
with UniProt ID UP000005640\_9606, was mapped.
For the epitopes that were present in the proteome exactly once,
the topology of the proteins in which these epitopes were located 
was predicted using both \verb;TMHMM; \cite{krogh2001predicting} 
and \verb;PureseqTM; \cite{wang2019efficient}. 
From this topology, we determined if the epitope
overlapped with a TMH.

>>>>

To obtain experimental evidence that epitopes derived from TMHs are presented in MHC,
we used two sources of data of naturally occurring epitopes.
The first type of data are two randomly picked 
peptide elution studies for MHC-I \cite{schellens2015comprehensive} 
and MHC-II \cite{bergseng2015different}.
The second type of data is obtained from IEDB, 
the Immune Epitope Databse \cite{vita2019immune}.
All these sources contain sequences of naturally occurring
epitopes. 
For each of the detected epitopes,
its possible location(s) in 
a human reference proteome,
with UniProt ID UP000005640\_9606, was mapped.
For the epitopes that were present in the proteome exactly once,
the topology of the proteins in which these epitopes were located 
was predicted using both \verb;TMHMM; \cite{krogh2001predicting} 
and \verb;PureseqTM; \cite{wang2019efficient}. 
From this topology, we determined if the epitope
overlapped with a TMH.
For IEDB, we queried for epitope sequences presented by B and T cells
in healthy humans, for the haplotypes used in this study.
